Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-09 msbr_reproc.tex
minor grammatical stuff

The \gls{MSBR} has the capability to remove every 20 seconds all poisons (e.g. 
$^{135}$Xe), noble metals and gases (e.g. $^{75}$Se, $^{85}$Kr) which also have 
relatively high absorption cross section. The thorium-232 absorbs thermal 
neutrons and produce $^{233}$Pa which then decay into the fissile $^{233}$U. 
The problem of protactinium is a large absorption cross section in the thermal 
energy spectrum, therefore $^{233}$Pa continuously removing from fuel salt into 
protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
reactor poisoning. The reactor reprocessing system designed to separate 
$^{233}$Pa from the molten-salt fuel over 3 days, held it to produce $^{233}$U 
and return it back to the primary loop. This feature allows to keep the 
neutrons losses to protactinium and fission products to a very low level, and 
increases the efficiency of $^{233}$U breeding \cite{robertson_conceptual_1971}.

>>>>

The \gls{MSBR} has the capability to remove all poisons
(e.g. 
$^{135}$Xe), noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) 
every 20 seconds. The $^{232}$Th in the fuel absorbs thermal 
neutrons and produces $^{233}$Pa which then decay into the fissile $^{233}$U. 
Protactinium presents a challenge, since it has a large absorption cross section in the thermal 
energy spectrum. Accordingly, $^{233}$Pa is continuously removed from fuel salt 
into a protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
reactor poisoning. The reactor reprocessing system designed to separate 
$^{233}$Pa from the molten-salt fuel over 3 days, held it to produce $^{233}$U 
and return it back to the primary loop. This feature allows to keep the 
neutrons losses to protactinium and fission products to a very low level, and 
increases the efficiency of $^{233}$U breeding \cite{robertson_conceptual_1971}.
